Nature or Nurture? Collisionless Evolution of Galactic Disc-Halo Systems

### 2019-07-27 Thesis/Background.tex
Updated thesis

\section{Phase Space, Equilibrium, and Initial Conditions} \label{sec:galaxy_ics}
In \S\ref{sec:motivation} we outlined the underlying theory behind representing stars and dark matter in an N-body simulation. The focus of this thesis is studying the behavior of stellar disks in cosmological environments, and the first step towards that understanding is the construction of a pristine, equilibrium N-body model. Ultimately, in the course of running an N-body simulation, these pristine systems will diverge to higher entropy\footnote{The Shannon entropy is a commonly used measure for self-gravitating systems. See \citet{BT} for more details.} states, initially due to random errors in the N-body representation. Nonetheless, these models give us an understanding of how perfectly unperturbed galaxies will evolve due to the fact that real galaxies are also made of a finite number of particles.

\subsection{Jeans Modelling and the Epicyclic Approximation}

@@

\subsection{DF-based Models and the Jeans Theorem}

@@

\section{Cosmology and Implications for Galaxy Studies} \label{sec:cosmology}
Our discussion up to this point has focused on simulating isolated systems. Complications arise when we move to a fully cosmological environment. The purpose of this section is to briefly review relevant cosmology, and to explain what numerical methods must be modified and used to simulate cosmological systems. We conclude this section with a brief commentary on identifying substructure in simulations.

\subsection{Simulations of FRW Cosmology: Large Scale Properties}

@@

Following up on this concept, we introduce the notion of \textit{redshift}. The term derives from the fact that as objects become more distant, we expect the hubble flow to cause the emitters to move away from the observer. Photons emitted by a stationary object with a wavelength, $\lambda$, are observed with wavelength $a(t_{emit}) \lambda$, and we define the redshift, $z$,
\begin{equation}
1 + z = \frac{1}{a}
\end{equation}
in analogy to this phenomenon. This is a descending unit of time that is often used interchangeably with the scale factor, $a$.
\subsection{Simulations of FRW Cosmology: Cosmological Initial Conditions}

@@

% Maybe say something about zoom-ins?
\subsection{Extension of Numerical Methods: Time Integration}

@@

\subsection{Extension of Numerical Methods: Gravity Calculation}

>>>>

\section{Phase Space and Initial Conditions} \label{sec:galaxy_ics}
In \S\ref{sec:motivation} we outlined the underlying theory behind representing stars and dark matter in an N-body simulation. The focus of this thesis is studying the behavior of stellar disks in cosmological environments, and the first step towards that understanding is the construction of a pristine, equilibrium N-body model. Ultimately, in the course of running an N-body simulation, these pristine systems will diverge to higher entropy\footnote{The Shannon entropy is a commonly used measure for self-gravitating systems. See \citet{BT} for more details.} states, initially due to random errors in the N-body representation. Nonetheless, these models give us an understanding of how perfectly unperturbed galaxies will evolve due to the fact that real galaxies are also made of a finite number of particles.

\subsection{Modelling Approaches}

@@

\subsection{DF-based Models}

@@

\section{Cosmology's Implications for Simulations} \label{sec:cosmology}
Our discussion up to this point has focused on simulating isolated systems. Complications arise when we move to a fully cosmological environment. The purpose of this section is to briefly review relevant cosmology, and to explain what numerical methods must be modified and used to simulate cosmological systems. We conclude this section with a brief commentary on identifying substructure in simulations.

\subsection{FRW Cosmology: Large Scale Properties}

@@

Following up on this concept, we introduce the notion of \textit{redshift}. The term derives from the fact that as objects become more distant, we expect the hubble flow to cause the emitters to move away from the observer. Photons emitted by a stationary object with a wavelength, $\lambda$, are observed with wavelength $a(t_{emit}) \lambda$, and we define the redshift, $z$,
\begin{equation}
1 + z = \frac{1}{a}
\end{equation}
in analogy to this phenomenon. This is a descending unit of time that is often used interchangeably with the scale factor, $a$.
\subsection{FRW Cosmology: Cosmological ICs}

@@

% Maybe say something about zoom-ins?
\subsection{Numerical Methods: Time Integration}

@@

\subsection{Numerical Methods: Gravity Calculation}
